---
title: "My Notebook"
output: html_notebook
---

# Data Analysis
For this analysis fixed effects regression is used. This kind of analysis allows us to control for time invariant unobservables.
An important feature as now we can control for (for example) personal characteristical trait biases from the analysis, or some "city-effect".

## Data
The subjective well-begin (SWB) data was collected by the german socio-economic panel (SEOP). The weather data stemms from the open-source 
project called meteostat. The two of them are combined into a single data set used for this analysis. In the following all the variables are listed:
```{r}
# importing libraries
library(RSQLite)
```
```{r}
# Relevant variables
vars <- c(
    # individual variables
    "pid", "health", "education",
    "gender", "birth_year", "relationship",
    "income_satisfaction", "swb",
    # house hold variables "hh_einkommen",
    "hh_children", "time", "hid",
    # weather variables
    "tavg", "tmin", "tmax", "prcp",
    "snow", "wdir", "wspd", "wpgt",
    "pres", "tsun",
    # location id
    "sloc"
)

# Create connection to database
conn <- dbConnect(RSQLite::SQLite(), "./prod/data.db")

# Load required data into df
df <- dbGetQuery(
    conn,
    sprintf('SELECT %s FROM "1_data" LIMIT 10;', paste(vars, collapse = ", "))
)
```
There are still quite some NaN values which need to be treated.


```{r}

```